My Past Work

### 2025-01-28 index.qmd
Update

Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 3rd year, double majoring in Sociology and Communications & New Media!

@@

For any opportunities, you can reach me via my email - marzukinooranas\@gmail.com or visit my [LinkedIn Page](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)

![](src/images/footer.png)

>>>>

Hello there! My name is Marzuki Nooranas \[[Resume](https://raw.githubusercontent.com/mrzknrns/mrzknrns.github.io/c446afc4b2d7902cfc76a22458cbc7789d1a09d7/MARZUKI_SANIP_RESUME.pdf)\] - or *Marz* for short! I am currently in my 3rd year, majoring in Sociology and Interactive Media Development!

@@

For any opportunities:

Email - marzukinooranas\@gmail.com

Linkedin - [Marzuki Nooranas](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)

Resume - [Download](https://raw.githubusercontent.com/mrzknrns/mrzknrns.github.io/c446afc4b2d7902cfc76a22458cbc7789d1a09d7/MARZUKI_SANIP_RESUME.pdf)

```         
```

### 2025-01-28 interests.qmd
Update

## National University of Singapore

### Digital Storytelling

@@

### Social Thought and Theory

@@

### Artificial Intelligence and Society

@@

### Temasek Polytechnic

### Savvify - An Automated Savings Platform

### GIGAWipes - Innovation through Programming

@@

![](src/images/footer.png)

>>>>

<br> I've dabbled in UX/UI design and video editing, mostly picking up these skills on my own because I'm really into it. I love creating cool user experiences and videos that pop, and I'm excited to keep leveling up and bringing more creativity to my work!

# UX/UI Prototyping and Design Work

## Interaction Design

### (1) SlideCraft - AI Powered Design Tool

SlideCraft is an AI-powered slide design tool created to simplify the presentation-making process for students and educators. I developed detailed lo-fi and hi-fi prototypes, focusing on features like design consistency, personalized recommendations, and efficiency.

This project emphasized enabling users to focus on content creation while saving time with AI-driven slide suggestions​

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share" allowfullscreen>

</iframe>

### (2) GPTDashboard - Desktop and Mobile View

The ChatGPT Dashboard was designed to help social media content creators streamline their workflow by integrating AI into content generation and tracking. I worked on both lo-fi and hi-fi prototypes, ensuring a smooth user experience across desktop and mobile views.

This project focused on addressing key pain points like burnout and content optimization while providing real-time feedback metrics to help creators stay on top of trends​

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-228&amp;starting-point-node-id=1%3A228&amp;embed-host=share" allowfullscreen>

</iframe>

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-155&amp;starting-point-node-id=1%3A155&amp;embed-host=share" allowfullscreen>

</iframe>

### (3) SaveWatt

SaveWatt is a digital platform aimed at helping homeowners make smarter, energy-efficient appliance choices amidst rising electricity tariffs. I contributed to the design of a user-friendly interface that consolidates appliance comparison tools, offering personalized recommendations and energy-saving insights.

This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way​

Full PortFolio: <https://savewatt.framer.website>

![](src/images/SaveWatt.png)

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&amp;node-id=89-2546&amp;starting-point-node-id=89%3A2546&amp;embed-host=share" allowfullscreen>

</iframe>

## TeachSG

For my TeachSG attachment, I created this motivational card specifically for primary school students who were struggling with math. The card was designed to inspire confidence and encourage them as they prepared for their PSLE exams.

Using bright colors, cheerful designs, and a personalized touch with mentor memojis, I aimed to make the card relatable and uplifting, helping the students feel supported and motivated to achieve their best.

::: {style="position: relative; width: 100%; height: 0; padding-top: 56.2225%; padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden; border-radius: 8px; will-change: transform;"}
<iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;" src="https://www.canva.com/design/DAGRwrKGhxo/DFyJSp72gAFRLvh1wU3bwA/view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">

<a href="https://www.canva.com/design/DAGRwrKGhxo/DFyJSp72gAFRLvh1wU3bwA/view?utm_content=DAGRwrKGhxo&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"></a>

## Artificial Intelligence and Society

# Video Editing and Production Work

## Savvify - An Automated Savings Platform

## Digital Storytelling

#### Pattoo Tarlour: The Art of the Needle

Here, we interviewed Pattoo Tarlour, a local tattoo business. We explored the artistry, passion, and personal stories behind tattooing in Singapore.

Through interviews with talented artists, visuals of their creative process, and dynamic shots capturing the parlour's ambiance, the documentary highlights the unique culture and meaningful connections that define the space. It celebrates the cultural and artistic significance of tattooing as both a craft and an expression of identity.

{{< video https://www.youtube.com/embed/AoD6FvMuHxk?si=t2d06a4Opw8NPRXV >}}

#### Day in the Life: Captured Through Film

@@

## Social Thought and Theory

@@

@@

## GIGAWipes - Innovation through Programming

@@
